Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-05 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:05	15:44:44	(Mon 5.Oct)

% 
% \begin{itemize}
% \item Dynamic weights $\Rightarrow$ greater contrast/resolution potential
% \item But:
% \begin{itemize}
% \item Active system $\Rightarrow$ noise and signal correlated $\Rightarrow$ adaptive beamformers no longer robust.
% \item Subarray averaging decorrelate the noise, but in the process we sacrifice resolution.
% \item Computationally complex O($M^3$) due to inversion of a spatial covariance matrix. LCA is only O($MW$). Even if Capon subspace/beamspace versions exist, they remain more complex than the LCA, and is not as ideally suited for implementation of SIMD hardware (GPUs, DSPs, ...).
% \end{itemize}
% \item LCA is inherently robust, is ``parameter free'' once setup with a well designed window set, and can often be implemented with minor modifications to already existing DAS beamformers.
% 
% The angular resolution and contrast in active sonar images depend on the beamformer's ability to receive signals from directions of interest, while suppressing noise and interference emanating from other directions. For sonar arrays, this is achieved by applying weights to the array channels.
% 
% While classical beamformers use predefined windows, adaptive beamformers estimate the optimal window by analytical evaluation of the data. The minimum variance (MV) beamformer, for instance, calculates the set of weights that minimises the variance of the beamformer's output. 
% 
We have implemented and studied the low complexity adaptive (LCA) beamformer in active sonar imaging. LCA is an attractive alternative to the minimum variance distortionless response (MVDR) method for minimizing noise and interference in sonar images. While MVDR estimates and inverts a spatial covariance matrix to compute an optimal window for the sonar array, LCA selects the optimal window from a predefined set using the same criterion as MVDR.

We show that a robust MVDR implementation typically chooses symmetric windows with responses in between that of the rectangular and Hamming window. When allowing LCA to choose from similar use Kaiser windows with similar responses to those of MVDR, and apply various amounts of steering. We find that when Steering to -3\,dB width of the window. This lead to a predictable resolution gain of . design LCA's window database with windows that resembles  constrained to work in active sonar imaging the typical window responses LCA is allowed to choose from windows that are typical solutions found by the minimum variance distortionless response (MVDR) method.

>>>>

% 
% \begin{itemize}
% \item Dynamic weights $\Rightarrow$ greater contrast/resolution potential
% \item But:
% \begin{itemize}
% \item Active system $\Rightarrow$ noise and signal correlated $\Rightarrow$ adaptive beamformers no longer robust.
% \item Subarray averaging decorrelate the noise, but in the process we sacrifice resolution.
% \item Computationally complex O($M^3$) due to inversion of a spatial covariance matrix. LCA is only O($MW$). Even if Capon subspace/beamspace versions exist, they remain more complex than the LCA, and is not as ideally suited for implementation of SIMD hardware (GPUs, DSPs, ...).
% \end{itemize}
% \item LCA is inherently robust, is ``parameter free'' once setup with a well designed window set, and can often be implemented with minor modifications to already existing DAS beamformers.
% 
% The angular resolution and contrast in active sonar images depend on the beamformer's ability to receive signals from directions of interest, while suppressing noise and interference emanating from other directions. For sonar arrays, this is achieved by applying weights to the array channels.
% 
% While classical beamformers use predefined windows, adaptive beamformers estimate the optimal window by analytical evaluation of the data. The minimum variance (MV) beamformer, for instance, calculates the set of weights that minimises the variance of the beamformer's output. 
% 
We have implemented and studied the low complexity adaptive (LCA) beamformer in active sonar imaging. LCA is an attractive alternative to the minimum variance distortionless response (MVDR) method for minimizing noise and interference in sonar images. While MVDR estimates and inverts a spatial covariance matrix to achieve this goal, LCA iterates through a predefined set of sensor weights selecting the one that best fulfills the minimum variance criterion.

We show that a robust MVDR implementation typically chooses windows with responses ranging between that of the rectangular and Hamming, or Kaiser windows with $\beta\in[0,2]$, respectively. We let LCA choose from these Kaiser windows with similar responses to those of MVDR, and apply some variations of steering to each, , . We find that when Steering to -3\,dB width of the window. This lead to a predictable resolution gain of . design LCA's window database with windows that resembles  constrained to work in active sonar imaging the typical window responses LCA is allowed to choose from windows that are typical solutions found by the minimum variance distortionless response (MVDR) method.
